---
title: "Polynomial Regression"
output: html_notebook
---

## Importing libraries

```{r}
#library(caTools)
library(ggplot2)
```

## Importing the dataset

```{r}
data <- read.csv(file = "A://Machine-Learning-A-Z/data/Position_Salaries.csv")
```

```{r}
data <- data[2:3]
```

## Splitting the dataset into training set and test set

```{r}
# set.seed(seed = 123)
# split <- sample.split(Y = data$Salary, SplitRatio = 0.8)
```

```{r}
# training_set <- subset(x = data, split == T)
# test_set <- subset(x = data, split == F)
```

## Fitting simple linear regression to the training set

```{r}
lin_reg <- lm(formula = Salary ~ Level, data = data)
```

```{r}
summary(lin_reg)
```

## Fitting polynomial linear regression to the training set

```{r}
data$Level2 <- data$Level^2
data$Level3 <- data$Level^3
data$Level4 <- data$Level^4
poly_reg <- lm(formula = Salary ~ ., data = data)
```

```{r}
summary(poly_reg)
```


## Visualizing the linear regression results

```{r}
ggplot() +
  geom_point(aes(x = data$Level, y = data$Salary),
             color = "red") +
  geom_line(aes(x = data$Level, y = predict(lin_reg, newdata = data)),
             color = "blue") +
  ggtitle("Truth or Bluff (Linear Regression)") +
  xlab("Level") +
  ylab("Salary")
```

## Visualizing the polynomial regression results

```{r}
ggplot() +
  geom_point(aes(x = data$Level, y = data$Salary),
             color = "red") +
  geom_line(aes(x = data$Level, y = predict(poly_reg, newdata = data)),
             color = "blue") +
  ggtitle("Truth or Bluff (Polynomial Regression)") +
  xlab("Level") +
  ylab("Salary")
```

## Predicting a new result with Linear Regression

```{r}
y_pred <- predict(lin_reg, newdata = data.frame(Level = 6.5))
y_pred
```

## Predicting a new result with Polynomial Regression

```{r}
y_pred <- predict(poly_reg, newdata = data.frame(Level = 6.5,
                                                 Level2 = 6.5^2,
                                                 Level3 = 6.5^3,
                                                 Level4 = 6.5^4))
y_pred
```


















